Competing Bandits: The Perils of Exploration under Competition

### 2018-08-30 paper/content/model.tex
Minor edits.

For ease of comparison, all three algorithms are parameterized with the same fake prior: namely, the mean reward of each arm is drawn independently from a Beta(1,1) distribution. Recall that Beta priors with 0-1 rewards form a conjugate family, which allows for simple posterior updates.

Both \DEG and \TS are classic MAB algorithms, see \cite{Bubeck-survey12,TS-survey-FTML18} for background. It is well-known that \TS is near-optimal in terms of the cumulative rewards, and \DEG is very suboptimal, but still much better than \DG.%
\footnote{Precise formulations, namely upper/lower bound on \emph{regret} of the three algorithms, are not very relevant to this paper.} In a formula:
    $ \TS \gg \DEG \gg \DG $
as stand-alone MAB algorithms.

>>>>

For ease of comparison, all three algorithms are parameterized with the same fake prior: namely, the mean reward of each arm is drawn independently from a $\Beta(1,1)$ distribution. Recall that Beta priors with 0-1 rewards form a conjugate family, which allows for simple posterior updates.

Both \DEG and \TS are classic MAB algorithms, see \cite{Bubeck-survey12,TS-survey-FTML18} for background. It is well-known that \TS is near-optimal in terms of the cumulative rewards, and \DEG is very suboptimal, but still much better than \DG.%
\footnote{Precise formulations, namely upper/lower bound on \emph{regret} of the three algorithms, are not very relevant to this paper.} In a stylized formula:
    $ \TS \gg \DEG \gg \DG $
as stand-alone MAB algorithms.
